|

### 2024-08-11 doc/paper.qmd
references update

**CFO**: Operating Cash Flow  
**EM**: Earnings Management  
**IDE**: Integrated Development Environment  
**UK**: United Kingdom  
**US**: United States  
**WRDS**: Wharton Research Data Services

@@

In line with the methodology used by @Leuz_2003, financial institutions were removed from the analysis based on their SIC codes. This was done by filtering out rows where the `item7021` identifier, representing the SIC code, falls within the range of 6000 to 6999. This ensures that the dataset focuses solely on non-financial companies.

>>>>

**CFO**: Operating Cash Flow  
**EM**: Earnings Management  
**IDE**: Integrated Development Environment  
**SIC**: Standard Industrial Classification  
**UK**: United Kingdom  
**US**: United States  
**WRDS**: Wharton Research Data Services

@@

In line with the methodology used by @Leuz_2003, financial institutions were removed from the analysis based on their Standard Industrial Classification (SIC) codes. This was done by filtering out rows where the `item7021` identifier, representing the SIC code, falls within the range of 6000 to 6999. This ensures that the dataset focuses solely on non-financial companies.
